\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-05 graph_abs.tex
incomplete commit of new abstraction section

\subsection{System under test ($\System$)}

We assume that $\System$ is a hybrid dynamical system with exogenous
inputs modeling an embedded control system. The system state-space
(denoted $\HybridStates$) is a subset of $\Modes \times \Reals^n$,
where $\Modes$ is a finite set of discrete modes, and $\Reals^n$
represents the continuous-valued state-space. For ease of exposition,
we assume that the hybrid system is effectively a switched-mode
dynamical system, \ie, the mode of the system is completely determined
by its state.  An input to $\System$ is assumed to be a time-bounded
{\em signal}, \ie, a function from $[0,T]$ to $\Inputs$, with $T$ as
the time horizon, and $\Inputs \subseteq \Reals^k$.  In this paper, we
view $\System$ as effectively black-box equipped with a forward
simulation map, in a simulation time-step of $\Delta_t$ from time $t$,
allows computing the unique reachable state $\vx \in \HybridStates$
given state-input pair $(\vx,\vu)$.

>>>>

\subsection{System-under-test ($\System$)}

We assume that the system-under-test is a hybrid dynamical system, \ie, a
system which has discrete modes and a continuous state-space, and which
evolvution is either (1) continuous in time according to the dynamics
associated with its current discrete mode (typically described using
differential equations over its continuous state), or (2) through
discrete jumps that possibly change the discrete mode of the system and
possibly reset its continuous state to some value.  However, we assume
that the system is {\em effectively black-box}. This means that we do not
assume any knowledge of the symbolic dynamical equations describing the
system behavior. We do assume some knowledge of the system: an {\em
interface} view, in which we are allowed to stimulate the system with
inputs and observe its outputs.

We formally define a system-under-test $\System$ as a tuple $(\Modes,
\ContStates, \initmode, \initstate, \Delta, \Inputs, \Outputs)$.  Here,
system state-space (denoted $\HybridStates$) is a subset of $\Modes \times
\ContStates$, where $\Modes$ is a finite set of discrete modes, and
$\ContStates$ is a compact subset of $\Reals^n$ representing the set of
continuous states.  We assume that the system is {\em initialized} to an
initial mode $\initmode$ and an initial state $\initstate$ at time $t=0$.
We assume that the system has $m$ exogenuous inputs which take values from
the set $\Inputs$ which is a compact subset of $\Reals^m$. We assume that
the system has $\ell \le n$ outputs, where $\Outputs \subseteq
\HybridStates$. In this paper, we assume that the entire system state is
observable.  In other words, $\Outputs = \HybridStates$.

Finally, we restrict our attention to switched-mode systems, \ie, those in
which there is a partition imposed on $\ContStates$, and there is a
bijective map between each element $\ContStates_i$ in the partition and
each mode in $\Modes$.

The operational semantics of $\System$ is defined in terms of a
forward-simulation map $\simmap_\Delta$, which is a function that maps a
time $t$, the current state of the system, and an input value in $\Inputs$
to the state of the system at time $t+\Delta$.

% We assume that $\System$ is a hybrid dynamical system with exogenous
% inputs modeling an embedded control system. 
% 
% we assume that the hybrid system is effectively a switched-mode
% dynamical system, \ie, the mode of the system is completely determined
% by its state.  An input to $\System$ is assumed to be a time-bounded
% {\em signal}, \ie, a function from $[0,T]$ to $\Inputs$, with $T$ as
% the time horizon, and $\Inputs \subseteq \Reals^k$.  In this paper, we
% view $\System$ as effectively black-box equipped with a forward
% simulation map, in a simulation time-step of $\Delta_t$ from time $t$,
% allows computing the unique reachable state $\vx \in \HybridStates$
% given state-input pair $(\vx,\vu)$.
